Concurrent Programming in Harmony

### 2021-12-22 book/paper.tex
Fixed some json escape issues

\section*{Exercises}
\begin{problems}
\item \label{ex:qcontains} Add a method $\mathtt{contains}(q, v)$ to \autoref{fig:queues}(b)
that checks to see if <{v}> is in queue <{q}>.
\item Add a method $\mathtt{length}(q)$ to \autoref{fig:queueconc} that returns the length of the given queue.
The complexity of the method should be $O(1)$, which is to say that you should maintain
the length of the queue as a field member and update it in <{put}> and <{get}>.
\item \label{ex:qlength} Write a method $\mathtt{check}(q)$
that checks the integrity of the queue in \autoref{fig:queueconc}.
In particular, it should check the following integrity properties:
\begin{itemize}
\item If the list is empty, <{q->tail}> should be <{None}>.
Otherwise, the last element in the linked list starting from <{q->head}>
should equal <{q->head}>. Moreover,
<{q->tail->next}> should be <{None}>;
\item The length field that you added in \autoref{ex:qlength} should equal the length
of the list.
\end{itemize}
Method <{check(q)>} should not obtain a lock; instead add the following line
just before releasing the lock in <{put}> and <{get}>:
<{:const:check}>
\begin{code}
<{assert check()}>
\end{code}
\item \label{ex:qremove} Add a method $\mathtt{remove}(q, v)$ to \autoref{fig:queueconc}
that removes all occurrences of <{v}>, if any, from queue <{q}>.
\item The test program in \autoref{fig:queuedemo} is a not thorough test program.
Design and implement a test program for \autoref{fig:queuedemo}.
Make sure you \emph{test} the test program by trying it out against some buggy
queue implementations.
\end{problems}

>>>>

\section*{Exercises}
\begin{problems}
\item \label{ex:qcontains} Add a method $\mathtt{contains}(q, v)$ to \autoref{fig:queues}(b)
that checks to see if <{v}> is in queue <{q}>.
\item Add a method $\mathtt{length}(q)$ to \autoref{fig:queueconc} that returns the length of the given queue.
The complexity of the method should be $O(1)$, which is to say that you should maintain
the length of the queue as a field member and update it in <{put}> and <{get}>.
\item \label{ex:qlength} Write a method $\mathtt{check}(q)$
that checks the integrity of the queue in \autoref{fig:queueconc}.
In particular, it should check the following integrity properties:
\begin{itemize}
\item If the list is empty, <{q->tail}> should be <{None}>.
Otherwise, the last element in the linked list starting from <{q->head}>
should equal <{q->head}>. Moreover,
<{q->tail->next}> should be <{None}>;
\item The length field that you added in \autoref{ex:qlength} should equal the length
of the list.
\end{itemize}
Method <{check(q)}> should not obtain a lock; instead add the following line
just before releasing the lock in <{put}> and <{get}>:
<{:const:check}>
\begin{code}
<{assert check()}>
\end{code}
\item \label{ex:qremove} Add a method $\mathtt{remove}(q, v)$ to \autoref{fig:queueconc}
that removes all occurrences of <{v}>, if any, from queue <{q}>.
\item The test program in \autoref{fig:queuedemo} is a not thorough test program.
Design and implement a test program for \autoref{fig:queuedemo}.
Make sure you \emph{test} the test program by trying it out against some buggy
queue implementations.
\end{problems}
